%-	Danh mục TL tham khảo
%-	Phụ lục (nếu có)
\textbf{Tiếng Anh}
\begin{thebibliography}{99}
\bibitem{ref-tiobe}
TIOBE 2020
\url{https://www.tiobe.com/tiobe-index/}, [Accessed 6 June 2020]
\bibitem{ref-mocha}
Mocha 2020
\url{https://mochajs.org/}, [Accessed 6 June 2020]
\bibitem{ref-jest}
Jest 2020
\url{https://jestjs.io/}, [Accessed 6 June 2020]
\bibitem{ref-jasmine}
Jasmine 2020
\url{https://jasmine.github.io/}, [Accessed 6 June 2020]
\bibitem{ref-dotup}
TypeScript Test Generator 2020
\url{https://marketplace.visualstudio.com/items?itemName=dotup.dotup-vscode-test-generator}, [Accessed 6 June 2020]

\bibitem{ref-jsTestGen}
JS Test Gen 2020
\url{https://js-test-gen.github.io/}, [Accessed 6 June 2020]

\bibitem{ref-factory}
Factory 2020
\url{https://www.npmjs.com/package/factory.ts}, [Accessed 6 June 2020]

\bibitem{ref-faker}
Faker 2020
\url{https://www.npmjs.com/package/faker}, [Accessed 6 June 2020]

\bibitem{ref-chance}
Chance 2020
\url{https://www.npmjs.com/package/chance}, [Accessed 6 June 2020]

\bibitem{ref-casual}
Casual 2020
\url{https://www.npmjs.com/package/casual}, [Accessed 6 June 2020]

\bibitem{ref-randexp}
Randexp 2020
\url{https://www.npmjs.com/package/randexp}, [Accessed 6 June 2020]

\bibitem{ref-sonarlint}
SonarLint 2020
\url{https://plugins.jetbrains.com/plugin/7973-sonarlint}, [Accessed 6 June 2020]

\bibitem{ref-tslint}
TSLint 2020
\url{https://palantir.github.io/tslint/}, [Accessed 6 June 2020]

\bibitem{ref-eslint}
ESLint 2020
\url{https://eslint.org/}, [Accessed 6 June 2020]

\bibitem{ref-instanbul}
Instanbul 2020
\url{https://istanbul.js.org/}, [Accessed 6 June 2020]
\bibitem{ref-jstool}
Witthaya Luanghirun, Taratip Suwannasart. 2016. Test Cases Generation Tool for JavaScript Based on Statement Coverage Criteria. In Proceedings of the International MultiConference of Engineers and Computer Scientists 2016 Vol I. IMECS 2016, March 16 - 18, 2016, Hong Kong
\bibitem{ref-symjs}
Guodong Li, Esben Andreasen, and Indradeep Ghosh. 2014. SymJS: automatic symbolic testing of JavaScript web applications. In Proceedings of the 22nd ACM SIGSOFT International Symposium on Foundations of Software Engineering (FSE 2014). Association for Computing Machinery, New York, NY, USA, 449–459.
% \bibitem{ref_rank1}
% Emerging Economies 2020
% \url{https://www.timeshighereducation.com/world-university-rankings/2020/emerging-economies-university-rankings}, 
\bibitem{unit-testing}
Adam D., \textit{The hitchhiker's guide to the galaxt}, San Val, 1995
\bibitem{Lee03}
Copeland Lee, \textit{A practitioner's guide to software test design}, Artech House, Inc., Norwood, MA, USA, 2003
\bibitem{ref-branch-coverage}
Karl J. Ottenstein. An algorithmic approach to the detection and prevention of plagiarism. \textit{ACM SIGSCE
Bulletin}, 8(4):30–41, 1976.
\bibitem{ref-cft4cunit}
Duc-Anh Nguyen and Pham Ngoc Hung. 2017. A Test Data Generation Method for C/C++ Projects. In Proceedings of the Eighth International Symposium on Information and Communication Technology (SoICT 2017). Association for Computing Machinery, New York, NY, USA, 431–438.
\bibitem{check3}
Sam Grier. A tool that detects plagiarism in Pascal programs. \textit{ACM SIGSCE Bulletin (Proc. of 12th
SIGSCE Technical Symp.)}, 13(1):15–20, February 1981.
\bibitem{check4}
K. K. Verco and M. J. Wise. Software for detecting suspected plagiarism: Comparing structure and
attribute-counting systems. In John Rosenberg, editor, \textit{Proc. of 1st Australian Conference on Computer
Science Education}, Sydney, July 1996.
\bibitem{yap3}
Michael J. Wise. Detection of similarities in student programs: YAP’ing may be preferable to Plague’ing.
\textit{ACM SIGSCE Bulletin (Proc. of 23rd SIGCSE Technical Symp.)}, 24(1):268–271, March 1992.
\bibitem{moss}
 Alex Aiken. MOSS (Measure Of Software Similarity) plagiarism detection system.
https://theory.stanford.edu/~aiken/moss/ (as of April 2000) and personal communication, 1998. University of Berkeley, CA.
\bibitem{algorithm}
Michael J. Wise. String similarity via greedy string tiling and running Karp-Rabin matching. Dept. of
CS, University of Sydney, ftp://ftp.cs.su.oz.au/michaelw/doc/RKR GST.ps, December 1993.
% \url{https://www.netacad.com/courses/packet-tracer}
% \bibitem{ref_tool2}
% Công cụ hỗ trợ chấm điểm input/output Verwandlung
% \url{https://github.com/hzxie/voj}
% \bibitem{ref_tool}
% Công cụ hỗ trợ chấm điểm input/output Verwandlung
% \url{https://github.com/hzxie/voj}
\bibitem{whitebox-testing}
Phạm Ngọc Hùng, Trương Anh Hoàng và Đặng Văn Hưng, "Giáo trình kiểm thử phần mềm", 2018.
\end{thebibliography}